Toxic Code Snippets on Stack Overflow

### 2018-05-24 cloverflow-tse/cover_letter/cover_letter.tex
Further changes to the cover letter.

\textbf{4.~An extended analysis of outdated code clones:}~We performed an
extended analysis of the 100 outdated code snippets. For example, we analysed
the age of the clones; studied effects of comments, newer answers, higher-voted
answers on the outdated answers; and summarised six intents that made the
clones outdated. We found that, on average, the outdated code snippets were cloned to Stack Overflow
2 years after it appeared in Qualitas projects, and comments/newer or
higher-voted answers did not strongly affect the outdated answers (99\% are
still marked as accepted). Lastly, we discovered that the code snippets are outdated
because of code enhancement (65\%), followed by code deprecation (15\%), but
fixing (10\%), code refactoring (6\%), changing coding style (3\%), and data
format change (2\%).

@@

\clearpage
We also tried our best to address all the comments from the reviewers. Every
comment led to an improvement on this submission, and we discuss them in order as
shown in the next sections.

Lastly, we would also like to ask the reviewers to comment on how to address the
newly established page limits of IEEE TSE that was enforced after our previous
submission. After incorporating the suggestions from the reviewers and
rewriting, our paper is now extended to 22 pages. Are there any elements that
could or should be removed, or should a split into two separate papers be
considered?

@@

\begin{enumerate} \item We understand the concern of finding real evidence to
	support the claim that code snippets on Stack Overflow do appear in open- or
	closed-source software projects. Hence, we have performed a study of code clone
	detection between our 100 reported outdated code snippets on Stack Overflow and
	131,703 GitHub projects. We selected SourcererCC with 80\% similarity for this
	experiment because it could scale to a large-scale data set, while Simian could
	not. We found 102 cloned candidates appearing in 68 GitHub projects and manually
	investigated all of them. As shown in Table~\ref{tab:outdated_github} below, out
	of the 102 cloned snippets, 13 cloned snippets matched with
	themselves because some of the Qualitas projects also appear on GitHub. For
	other projects besides the Qualitas projects, 47 cloned snippets
	were exactly the same as the outdated code snippet and 42 cloned snippets that
	were not the same (e.g.,~they contained additional code modifications
	made by the projects' developers, or they were copied from another source with a
	slightly different code).

@@

Among the exact-copy of 47 outdated cloned snippets, there were only two cloned
snippets that gave attributions to Stack Overflow. However, the attributions
pointed to different posts than the ones we found but containing the same code
in the answers. The other 32 cloned snippets were very likely to be a
file-level clone from its respective original project (e.g.,~JFreeChart, JUnit,
Log4J, Hadoop) based on their license header and the Javadoc comments. Lastly,
the remaining 13 cloned snippets did not have any hints or evidence of copying.
Twelve of them were toxic because they were the old versions that still
contained bugs.

@@

We partially address this comment in the previous answer by performing an
empirical study of code cloning between toxic Stack Overflow code snippets and
GitHub projects. Furthermore, we also improved the paper on the aspect of the
awareness of information-seekers to toxic code snippets on Stack Overflow by
including the results from another survey of Stack Overflow visitors
(i.e.,~information seekers). This survey of the Stack Overflow visitors was
performed during the same time as the Stack Overflow answerers (25 July 2017 to
25 September 2017), and the full results are reported in our technical
report~\citep{Ragkhitwetsagul_RN2017}. We did not include the results in the
previous version of the paper due to a smaller sample size compared to the
answerers' survey. However, we did find some interesting results, so we have
included them in this version and discussed the key findings in~RQ1. The brief
summary of the visitor survey is as follows.

@@

	\item We improved the Actionable Items to be more precise about the mechanics
	on how to automate the process of finding online code clones, detecting
	outdated code, and finding license-incompatible code snippets.

@@

\rcomment{ Other Comments While ``Toxic Code Snippets'' is a catchy phrase for
	the title, I think that online code clones are the dominant topic.}

@@

Regarding RQ4 (Software licensing violation), it needs to follow RQ 1--2 because
the license violation needs evidence of cloning direction. To put it another
way, we could tell that the code snippets on Stack Overflow may have
incompatible licenses to their originals after we confirmed that (1) the Stack
Overflow code snippets were actually clones of Qualitas projects and (2) the
direction of cloning was from Qualitas to Stack Overflow, which both are
addressed in RQ1 and RQ2. Nevertheless, RQ4 does not need to follow RQ3
(Outdated online code clones) because they are independent of each other.

@@

To measure the impact of this minimum clone size threshold on the clone results,
we performed an investigation of three different threshold values: six, ten, and
fifteen lines. We started our investigation by using a threshold value of six
lines, a well-accepted minimum clone size in clone benchmark~\citep{Bellon2007}.
Simian reported 67,172 clone candidate pairs and SourcererCC reported 7,752
clone candidate pairs. We randomly sampled 382 pairs from the two sets for
a manual check. This sample number was a statistically significant sample with a
95\% confidence level and $\pm 5\%$ confidence interval. The first author
investigated the sampled clone pairs and classified them into three groups:
non-clones, trivial clones (\texttt{equals}, \texttt{hashCode}, or getter and
setter methods), and non-trivial clones. The manual check found 26 non-clone
pairs; 322 trivial clone pairs, and 34 non-trivial clone pairs. Next, we
increased the threshold to ten lines, another well-established minimum clone
size for large-scale data sets~\cite{Sajnani2016}, and retrieved 721 clone pairs
from Simian and 1,678 clone pairs from SourcererCC. We randomly sampled and
manually checked the same amount of 382 pairs and found 27 non-clone pairs, 253
trivial clone pairs, and 102 non-trivial clone pairs. Then, we increased the
threshold further to fifteen lines and retrieved 196 clone pairs from Simian and
1,230 clone pairs from SourcererCC. The manual check of the 382 randomly sampled
pairs revealed zero non-clone pairs, 298 trivial clone pairs, and 83 non-trivial
clone pairs.

The findings from the three threshold values show that selecting the minimum
clone size of ten lines was preferred over six and fifteen lines. First, it
generated a fewer number of clone pairs than using six lines, which made the
manual clone investigation feasible. Second, it preserved the highest number of
non-trivial clone pairs.

We have modified the paper to include this discussion at the end of Section
2.2.1.

@@

To summarise, we empirically show from the surveys and the clone detection
experiment that online code clones occur on Stack Overflow and the clones may
become toxic due to outdated code and software license incompatibility. For
outdated code, we found only a small number of clones. Although other studies
show that Stack Overflow code snippets may contain security
vulnerabilities~\citep{Acar2016,Fischer2017} or API misuse~\citep{Zhang2018}, we
found in this study that the damage caused by reusing outdated code on Stack
Overflow is not high. On the other hand, the missing licensing statements of
online code clones on Stack Overflow can be more harmful. As shown in our study
and also in the study by \cite{An2017}, some online clones on Stack Overflow are
originally licensed under more restrictive license than Stack Overflow's CC
BY-SA 3.0. If these missing-license online clones are reused in software with
an incompatible license, the software owner may face legal issues. Software
auditing services such as Black Duck Software or nexB, which can effectively
check for license compliance of code copied from open source projects, do not
check for the original license of the code snippets on Stack Overflow. Although
the Stack Overflow answerers who participated in our survey believe that most of
the code snippets on Stack Overflow are too small to claim for copyright and
they fall under fair-use, there is still a risk due to different legal systems
in each country. For example, Germany's legal system does not have a concept of
fair use or the number of minimum lines of code to be considered trivial,
i.e.,~de minimis, is also different from case to case or from country to country.

We also updated the Actionable Items section to reflect Reviewer 1's comment.

@@

\section{Conclusion}
We would like to thank the reviewers again for their comments.
We have tried our best to address every concern that has been pointed out by the reviewers. This result in inclusion of a Stack Overflow visitors' survey, an analysis of toxic code snippets in GitHub projects, analysis of different tools' and technique's parameters, a more detailed analysis of online code clones, the updated definition of toxic code snippets, the improved overall discussion section, and other minor improvements throughout the paper.
We believe this new submission has been considerably improved from the previous version due to the insightful reviews and discussions and we are looking forward to the new reviews.

>>>>

\textbf{4.~An extended analysis of outdated code clones:}~We performed an
extended analysis of the 100 outdated code snippets. For example, we analysed
the age of the clones; studied the effects of comments, newer answers, and higher-voted
answers on the outdated answers; and summarised six intents that made the
clones outdated. We found that, on average, the outdated code snippets were cloned to Stack Overflow
2 years after it appeared in Qualitas projects, and comments/newer or
higher-voted answers did not strongly affect the outdated answers (99\% are
still marked as accepted). Lastly, we discovered that the code snippets are outdated
because of code enhancement (65\%), followed by code deprecation (15\%), but
fixing (10\%), code refactoring (6\%), changing coding style (3\%), and data
format change (2\%).

@@

\clearpage
We tried our best to address all the comments from the reviewers. Every
comment led to an improvement on this submission, and we discuss them in order as
shown in the next sections.

Lastly, we would also like to ask the reviewers to comment on how to address the
newly established page limits of IEEE TSE that was enforced on 18 February 2018, after our previous
submission (15 November 2017). After incorporating the suggestions from the reviewers and
rewriting, our paper is now extended to 22 pages. Are there any elements that
could or should be removed, or should a split into two separate papers be
considered?

@@

\begin{enumerate} \item We understand the concern of finding real evidence to
	support the claim that code snippets on Stack Overflow do appear in open- or
	closed-source software projects. Hence, we have performed a study of code clone
	detection between our 100 reported outdated code snippets on Stack Overflow and
	131,703 GitHub projects. We selected SourcererCC with 80\% similarity for this
	experiment because it could scale to a large-scale data set, while Simian could
	not. We found 102 cloned candidates appearing in 68 GitHub projects and manually
	investigated all of them. As shown in Table~\ref{tab:outdated_github} below, out
	of the 102 cloned snippets, 13 cloned snippets matched with
	themselves because some of the Qualitas projects also appear on GitHub. For
	other projects besides the Qualitas projects, 47 cloned snippets
	were the same as the outdated code snippet, and 42 cloned snippets
	were not the same (e.g.,~they contained additional code modifications
	made by the projects' developers, or they were copied from another source with a
	slightly different code).

@@

Among the exact-copy of 47 outdated cloned snippets, there were only two cloned
snippets that gave attributions to Stack Overflow. However, the attributions
pointed to different posts than the ones we found but containing the same code
in the answers (the answers were not marked as accepted so they were not included in our experiment). 
The other 32 cloned snippets were very likely to be a
file-level clone from its respective original project (e.g.,~JFreeChart, JUnit,
Log4J, Hadoop) based on their license header and the Javadoc comments. Lastly,
the remaining 13 cloned snippets did not have any hints or evidence of copying.
Twelve of them were toxic because they were the old versions that still
contained bugs.

@@

We partially address this comment in the previous answer by performing an
empirical study of code cloning between toxic Stack Overflow code snippets and
GitHub projects. Furthermore, we also improved the paper on the aspect of the
awareness of information-seekers to toxic code snippets on Stack Overflow by
including the results from another survey of Stack Overflow visitors
(i.e.,~information seekers). This survey of the Stack Overflow visitors was
performed during the same time as the Stack Overflow answerers (25 July 2017 to
25 September 2017), and the full results are reported in our research note~\citep{Ragkhitwetsagul_RN2017}. 
We did not include the results in the
previous version of the paper due to a smaller sample size compared to the
answerers' survey. However, we did find some interesting results, so we have
included them in this version and discussed the key findings in~RQ1. The brief
summary of the visitor survey is as follows.

@@

	\item We improved the Actionable Items to be more precise about the mechanics
	on how to automate the process of finding online code clones, detecting
	outdated code, and finding license-incompatible code snippets as the means
	to mitigate the problems from toxic code snippets.

@@

\rcomment{ Other Comments:\newline While ``Toxic Code Snippets'' is a catchy phrase for
	the title, I think that online code clones are the dominant topic.}

@@

Regarding RQ4 (Software licensing violation), it needs to follow RQ 1--2 because
the license violation needs evidence of cloning direction. To put it another
way, we could tell that the code snippets on Stack Overflow may have
incompatible licenses to their originals after we confirmed that (1) the Stack
Overflow code snippets were actually clones of Qualitas projects and (2) the
direction of cloning was from Qualitas to Stack Overflow, which are both
addressed in RQ1 and RQ2. Nevertheless, RQ4 does not need to follow RQ3
(Outdated online code clones) because they are independent of each other.

@@

To measure the impact of this minimum clone size threshold on the clone results,
we performed an investigation of three different threshold values: six, ten, and
fifteen lines. We started our investigation by using a threshold value of six
lines, a well-accepted minimum clone size in clone benchmark~\citep{Bellon2007}.
Simian reported 67,172 clone candidate pairs and SourcererCC reported 7,752
clone candidate pairs. We randomly sampled 382 pairs from the two sets for
a manual check. This sample number was a statistically significant sample with a
95\% confidence level and $\pm 5\%$ confidence interval. The first author
investigated the sampled clone pairs and classified them into three groups:
non-clones, trivial clones (\texttt{equals}, \texttt{hashCode}, or getter and
setter methods), and non-trivial clones. The manual check found 26 non-clone
pairs; 322 trivial clone pairs, and 34 non-trivial clone pairs. Next, we
increased the threshold to ten lines, another well-established minimum clone
size for large-scale data sets~\citep{Sajnani2016}, and retrieved 721 clone pairs
from Simian and 1,678 clone pairs from SourcererCC. We randomly sampled and
manually checked the same amount of 382 pairs and found 27 non-clone pairs, 253
trivial clone pairs, and 102 non-trivial clone pairs. Then, we increased the
threshold further to fifteen lines and retrieved 196 clone pairs from Simian and
1,230 clone pairs from SourcererCC. The manual check of the 382 randomly sampled
pairs revealed zero non-clone pairs, 298 trivial clone pairs, and 83 non-trivial
clone pairs.

The findings from the three threshold values show that selecting the minimum
clone size of ten lines was preferred over six and fifteen lines. First, it
generated a fewer number of clone pairs than using six lines, which made the
manual clone investigation feasible. Second, it preserved the highest number of
non-trivial clone pairs.
We have modified the paper to include this discussion at the end of Section
2.2.1.

@@

To summarise, we empirically show from the surveys and the clone detection
experiment that online code clones occur on Stack Overflow and the clones may
become toxic due to outdated code and software license incompatibility. For
outdated code, we found only a small number of clones. Although other studies
show that Stack Overflow code snippets may contain security
vulnerabilities~\citep{Acar2016,Fischer2017} or API misuse~\citep{Zhang2018}, we
found in this study that the damage caused by reusing outdated code on Stack
Overflow is not high. On the other hand, the missing licensing statements of
online code clones on Stack Overflow can be more harmful. As shown in our study
and also in the study by \cite{An2017}, some online clones on Stack Overflow are
originally licensed under more restrictive license than Stack Overflow's CC
BY-SA 3.0. If these missing-license online clones are reused in software with
an incompatible license, the software owner may face legal issues. Software
auditing services such as Black Duck Software or nexB, which can effectively
check for license compliance of code copied from open source projects, do not
check for the original license of the code snippets on Stack Overflow. Although
the Stack Overflow answerers who participated in our survey believe that most of
the code snippets on Stack Overflow are too small to claim for copyright and
they fall under fair-use, there is still a risk due to different legal systems
in each country. For example, Germany's legal system does not have a concept of
fair use. The number of minimum lines of code to be considered trivial,
i.e.,~de minimis, is also different from case to case or from country to country.
Lastly, we also updated the Actionable Items section to reflect Reviewer 1's comment.

@@

\section{Conclusion}
We would like to thank the reviewers again for their comments.
We have tried our best to address every concern that has been pointed out by the reviewers. This result in inclusion of a Stack Overflow visitors' survey, an analysis of toxic code snippets in GitHub projects, analysis of different tools' and technique's parameters, a more detailed analysis of online code clones, the updated definition of toxic code snippets, the improved overall discussion section, and other minor improvements throughout the paper.
We believe this new submission has been considerably improved from the previous version due to the insightful reviews and discussions. We are looking forward to the new reviews.
